Hypertension and microbiome

### 2019-05-16 articletwo.Rmd
Line change

```{r check odds model assumptions}
g.odds.autoplot <- autoplot(glm.hypertension.lactogroup,
                            which = 1:4,
                            nrow = 1,
                            ncol = 2,
                            label.size = 3,
                            size = 0.1) +
    theme_minimal()
ggsave(file = "cache/odds-autoplot.png", plot=g.odds.autoplot, height=10, width=6, dpi = 300)

>>>>

```{r check odds model assumptions}
g.odds.autoplot <- autoplot(glm.hypertension.lactogroup,
                            which = 1:4,
                            nrow = 1,
                            ncol = 2,
                            label.size = 3,
                            size = 0.1) +
    theme_minimal()
ggsave(file = "cache/odds-autoplot.png", plot=g.odds.autoplot, height=10, width=6, dpi = 300)
```
